Accessing the nucleon tensor structure in inclusive deep inelastic scattering

### 2016-07-19 1607 - JMC for g2/Paper/JMC_dis.tex
New title
Started reviewing typos, and other small things - figure added

\usepackage[tbtags]{amsmath}  % AMS math 
\usepackage{amssymb}          % AMS symbols
\usepackage{bm}               % bold math
\usepackage{graphicx}         % PostScript figures
\usepackage{hhline,multirow}  % for nicer tables
\usepackage{dcolumn}          % Align table columns on decimal point
\usepackage{slashed}
\usepackage{datetime}

%%%%%% for draft
\newcommand{\todo}[1]{\marginpar{$\bullet$}\textbf{#1}}

@@

\title{A novel chiral consedate contribution in inclusive deep inelastic scattering}

@@

The correlator $\Xi$ can be parametrized in terms of scalar functions, using the vectors $l$ and $n_+$ 
\begin{equation}
\Xi(l,n_+) = \Lambda A_1(l^2)\,{\bm 1} + A_2(l^2)\,\lslash 
+ \frac{\Lambda^2}{l \cdot n_{+}} \nslash_+ \, B_{1}(l^2)
+ \frac{i \Lambda}{2 P \cdot n_{+}} [\,\lslash,\nslash_+ ] \, B_{2}(l^2) \ .
\label{e:jetexpansion}
\end{equation} 
Time reversal invariance in QCD requires $B_{2}=0$, while $B_{1}$ contributes
only at twist-4 order, and will not be considered further in this paper. We
focus on the role of chiral odd terms in the $g_2$ structure function up to
twist 3.  At this order, 
\begin{equation}
  \Xi(l,n_+) = \Lambda A_1(l^2)\,{\bm 1} + A_2(l^2)\,\lslash 
    + O(\Lambda/Q^2)
\label{e:jetexpansion-tw3}
\end{equation} 
is nothing else than the full quark propagator; note however, that we consider
here the full QCD vacuum rather than the perturbative one.

The $A_1$ and $A_2$ terms can be nicely interpreted in terms of the spectral representation of the cut quark propagator,
\begin{align} 
  \Xi(l) =  
  \int d \mu^2 \big[ J_1 (\mu^2)\,\mu + J_2 (\mu^2)\,\lslash \big] \,
  \delta(l^2 -m_j^2) \ ,
\label{e:jetspectral}
\end{align}
where $\mu^2$ is interpreted as the invariant mass of the current jet, {\it i.e.}, of the particles going through the cut in the top blob of Fig.\ref{fig:handabgs}(a), and the $J_i$ are the spectral functions of the quark propagator, that have been also called ``jet functions'' in \cite{Accardi-Qiu}. These satisfy \cite{D'Hoker-lecture-notes,Romao-lecture-notes}
\begin{align}
  J_2(\mu^2) \geq J_1(\mu^2) \geq 0
  \hspace*{0.5cm} \text{and} \hspace*{0.5cm}
  \int d\mu^2 J_2(\mu^2) = 1 \ .
\label{eq:jetfnsprops}
\end{align}
From a comparison of Eqns.\eqref{e:jetexpansion} and \eqref{e:jetspectral}, one can see that 
\begin{align}
  A_1(l^2)&=\frac{\sqrt{l^2}}{\Lambda}J_1(l^2) & A_2(l^2)&=J_2(l^2) \ .
  \label{eq:jet_vs_spectral}
\end{align}

When inserting the jet correlator in the handbag diagram for inclusive DIS, the invariant jet mass $\mu^2$ is integrated from 0 to $Q^2(1/x_B-1)$. This induces (kinematical) corrections of order $O(1/Q^2)$, whose effect on the $F_2$ structure function has been studied in Ref.~\cite{Accardi-Qiu}. In this paper we limit our attention to effects of order $O(1/Q)$ and therefore can extend the integration to $\mu^2=\infty$. For example, the unpolarized DIS structure function $F_2$ reads

@@

  F_2(x_B) & = \int_0^{Q^2(1/x_B-1)}d\mu^2\, J_2(\mu^2) F_2^{(0)}(x_B(1+\mu^2/Q^2),Q^2)  \\
  & = \Big( \int_0^\infty d\mu^2\, J_2(\mu^2) \Big) F_2^{(0)}(x_B,Q^2) 
     + O(\Lambda^2/Q^2) \\
  & = F_2^{(0)}(x_B,Q^2)  + O(\Lambda^2/Q^2) \ ,

@@

where $F_2^{(0)}$ is the structure function calculated with the handbag diagram sporting a bare quark propagator instead of the jet correlator.
At this order the jet function $J_2$ decouples and thanks to the sum rule \eqref{eq:jetfnsprops} it integrates to 1, so that one recovers the conventional result. The same holds true also for the helicity structure function $g_1$.

@@

More in general, the jet correlator decouples from the parton correlator $\Phi$ in inclusive cross section calculation up to $O(1/Q)$, on which we are focusing the attention in this paper, and the inclusive structure functions depend on the integrated jet correlator

@@

  \Xi \equiv \int \frac{dl^2}{2l^-} d^2 l_T \, \Xi(l) 

@@

>>>>

\usepackage[tbtags]{amsmath}  % AMS math 
\usepackage{amssymb}          % AMS symbols
\usepackage{bm}               % bold math
\usepackage{graphicx}         % PostScript figures
\usepackage[export]{adjustbox}% to align images
\usepackage{hhline,multirow}  % for nicer tables
\usepackage{dcolumn}          % Align table columns on decimal point
\usepackage{slashed}
\usepackage{datetime}
\usepackage{color}
\usepackage[dvipsnames]{xcolor}

%%%%%% for draft
\newcommand{\todo}[1]{\marginpar{$\bullet$}\textbf{#1}}
\def\AAcom#1{{\bf  \textcolor{Red}{[AA: {#1}]}}}
\def\AAmod#1{{\textcolor{Green}{#1}}}

@@

\title{Accessing the nucleon tensor structure in inclusive deep inelastic scattering}

@@

\begin{figure*}
  \centering
  (a)\includegraphics[width=0.3\linewidth,valign=t]{jetdiagram0}
  \hfill
  (b)\includegraphics[width=0.3\linewidth,valign=t]{jetdiagram1}
  \hfill
  (c)\includegraphics[width=0.3\linewidth,valign=t]{jetdiagram2}
  \caption{Diagrams contributing to DIS scattering up to twist-3 expansion, including a jet correlator in the top part. Note the gluon attaches to both the nucleon and jet correlators. The Hermitian conjugates of diagrams (b) and (c), i.e., with gluons attaching to the right of the cut, are not shown.
  }
  \label{fig:handbags}
\end{figure*}

The correlator $\Xi$ can be parametrized in terms of scalar functions, using the vectors $l$ and $n_+$ 
\begin{equation}
\Xi(l,n_+) = \Lambda A_1(l^2)\,{\bm 1} + A_2(l^2)\,\lslash 
+ \frac{\Lambda^2}{l \cdot n_{+}} \nslash_+ \, B_{1}(l^2)
+ \frac{i \Lambda}{2 P \cdot n_{+}} [\,\lslash,\nslash_+ ] \, B_{2}(l^2) \ .
\label{e:jetexpansion}
\end{equation} 
Time reversal invariance in QCD requires $B_{2}=0$, while $B_{1}$ contributes
only at twist-4 order, and will not be considered further in this paper. We
focus on the role of chiral odd terms in the $g_2$ structure function up to
twist 3.  At this order, 
\begin{equation}
  \Xi(l,n_+) = \Lambda A_1(l^2)\,{\bm 1} + A_2(l^2)\,\lslash 
    + O(\Lambda^2/Q^2)
\label{e:jetexpansion-tw3}
\end{equation} 
is nothing else than the full quark propagator; note however, that we consider
here the full QCD vacuum rather than the perturbative one.

The $A_1$ and $A_2$ terms can be nicely interpreted in terms of the spectral representation of the cut quark propagator,
\begin{align} 
  \Xi(l) =  
  \int d \mu^2 \big[ J_1 (\mu^2)\,\mu + J_2 (\mu^2)\,\lslash \big] \,
  \delta(l^2 -\mu_j^2) \ ,
\label{e:jetspectral}
\end{align}
where $\mu^2$ is interpreted as the invariant mass of the current jet, {\it i.e.}, of the particles going through the cut in the top blob of Fig.\ref{fig:handabgs}(a), and the $J_i$ are the spectral functions of the quark propagator, that have been also called ``jet functions'' in \cite{Accardi-Qiu}. These satisfy \cite{D'Hoker-lecture-notes,Romao-lecture-notes}
\begin{align}
  J_2(\mu^2) \geq J_1(\mu^2) \geq 0
  \hspace*{0.5cm} \text{and} \hspace*{0.5cm}
  \int d\mu^2 J_2(\mu^2) = 1 \ .
\label{eq:jetfnsprops}
\end{align}
From a comparison of Eqns.\eqref{e:jetexpansion} and \eqref{e:jetspectral}, one can see that 
\begin{align}
  A_1(l^2)&=\frac{\sqrt{l^2}}{\Lambda}J_1(l^2) & A_2(l^2)&=J_2(l^2) \ .
  \label{eq:jet_vs_spectral}
\end{align}

When inserting the jet correlator in the handbag diagram for inclusive DIS, the invariant jet mass $\mu^2$ is integrated from 0 to $Q^2(1/x_B-1)$. This induces (kinematical) corrections of order $O(1/Q^2)$, whose effect on the $F_2$ structure function has been studied in Ref.~\cite{Accardi-Qiu}; for example, 
teh structure function $F_2$ reads

@@

  F_2(x_B) & = \int_0^{Q^2(1/x_B-1)}d\mu^2\, J_2(\mu^2) F_2^{(0)}(x_B(1+\mu^2/Q^2),Q^2) \ ,

@@

where $F_2^{(0)}$ is the structure function calculated with the handbag diagram sporting a bare quark propagator instead of the jet correlator, and $\xi=2x_B/(1+\sqrt{1+4x_B^2M^2/Q^2})$ with $M$ the nucleon's mass is the Nachtmann scaling variable.  In this paper we limit our attention to effects of order $O(1/Q)$ and therefore can extend the integration to $\mu^2=\infty$. Therefore jet function $J_2$ decouples, and thanks to the sum rule \eqref{eq:jetfnsprops} integrates to 1. One then recovers the conventional result.
  F_2(x_B) = \Big[ \int_0^\infty d\mu^2\, J_2(\mu^2) \Big] F_2^{(0)}(x_B,Q^2) 
     + O(\Lambda^2/Q^2) = F_2^{(0)}(x_B,Q^2)  + O(\Lambda^2/Q^2) \ .
The same holds true also for the helicity structure function $g_1$.

@@

More in general, the jet correlator decouples from the parton correlator $\Phi$ in any inclusive cross section calculation up to $O(1/Q)$, and the inclusive structure functions only depend on the integrated jet correlator

@@

  \Xi(l^-) \equiv \int \frac{dl^2}{2l^-} d^2 l_T \, \Xi(l) 

@@

\AAcom{We need to discuss what happens to the B functions!! See e-mail from Jul 7th, 2015, for ideas.}
